### 2015-04-19 zoldatoff/tex/text retrieval/lecture10.tex
Лекции по курсу Text Retrieval
Неделя 4. Лекции 5-8

>>>>

%---------------------------------------------
\subsection{Future of Web Search}

\subsubsection{Next Generation Search Engines}
\begin{itemize}
\item More specialized/customized (vertical search engines):
\begin{itemize}
\item Special group of users (community engines, e.g., Citeseer) 
\item Personalized (better understanding of users)
\item Special genre/domain (better understanding of documents)
\end{itemize}

\item Learning over time (evolving)
\item Integration of search, navigation, and recommendation/filtering
(full-fledged information management)
\item Beyond search to support tasks (e.g., shopping)
\item Many opportunities for innovations!
\end{itemize}

\subsubsection{Future Intelligent Information Systems}
\begin{itemize}
\item Search $\Rightarrow$ Access $\Rightarrow$ Mining $\Rightarrow$ Task support
\item Keyword queries $\Rightarrow$ Search history $\Rightarrow$ Complete user model
\item Bag of words $\Rightarrow$ Entities-Relations $\Rightarrow$ Knowledge presentation
\end{itemize}
